---
title: "Discussion on End of Project Strategy"
author: "Collin Schwantes"
date: '`r Sys.Date()`'
output: 
  ehastyle::eha_avenir_pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(officedown)
library(ggplot2)
library(rvg)
library(ehastyle)
```

## Introduction

-  Ending projects properly ensures compliance with award obligations, supports proper management of resources, and facilitates reuse of research outputs (code, data, protocols, etc). 
- Creating reusable research outputs increases research impact
- Primary beneficiary will be you. 

## Goals of today's discussion

- Provide an overview of planned strategy
- Understand where plan might break down
- Determine whats training or infrastructure is needed


## Overview of strategy

- FAIR data products

## Overview of Strategy

- Data management plans

## Overview of Strategy

- Asset management

## Overview of Strategy

- metadata - code and data

## Overview of Strategy

- divorcing pbulication of results from publication of data and code
- 

## Overview of Strategy

- Mechanics of process 
- roles and responsbilities 
## Slide to the Right 

:::::: {.columns}
::: {.column}
Use `layout='Two Content', ph=officer::ph_location_right()` 
to properly place content 
:::

::: {.column}

```{r righttable, layout='Two Content',ph=officer::ph_location_right()}
head(cars,10)
```
:::
::::::

## Slide to the left 

:::::: {.columns}
::: {.column}
```{r layout='Two Content', ph=officer::ph_location_left()}
head(cars)
```
:::

::: {.column}
- Left side table
:::
::::::

##  Slide with SVG Plot

```{r pressure}
## use dml to make the plot an editable svg in ppt
dml(plot(pressure))
```

## Slide with SVG Ggplot

```{r }
ggplotObj <- ggplot(mtcars, aes(wt, mpg), col = displ) +
  geom_point()

## pass a ggplot object to dml 
dml(ggobj = ggplotObj)
```
